This body of work encompasses seven years of effort that would not have been
possible without the professional and emotional support of my friends, family,
and newfound colleagues. I declare my immense thanks to them for the
following reasons.

First, to my family:\\
The continuous pride and understanding that my family has expressed in regards
to the pursuit of my doctorate has been the driving force behind my stalwart
efforts these past few years. They have continued to champion my marathon
despite my long-awaited presence at the finish line. And during the times of despair
and frustration that commonly plague scientific research, I have always been
able to benefit from the respite that I received in the sanctuaries that were
their homes. To all of them, I convey my eternal gratitude and love.

To my colleague, friend, and mentor - Jin Montclare:\\
From day one, you have continued to foster and promote my advancement as a
scientist and intellectual. Assuredly, I am a better person for it.  We have
celebrated academic successes as well as suffered scientific and professional
tribulations. But perhaps most importantly, regardless of the context, you have
undoubtedly and consistently demonstrated your utmost trust in both my abilities
and my character - a privilege for which I can only hope I have abundantly
reciprocated in kind. Thank you very much for the momentous opportunity to have
worked with you.

To my colleagues:\\
There are many individuals to whom I owe thanks for their professional support
during the course of my doctoral studies. They include fellow students (high
school, undergraduate, and graduate alike), accomplished scientists, aspiring
professors, and university administrators and staff. A vast majority of them
have provided me with an infinitely expansive sounding board for my ideas and
have in turn stimulated the advancement of my research. Others have quelled
quagmires before they escalated toward affecting the completion of my degree.
And others have simply promoted my advancement as a research scientist through
the extension of rare professional opportunities. 

To my close friends:\\
I submit my sincerest apologies, more so and in addition to my gratitude. A
graduate career of seven years has in truth robbed me of many occasions to spend
with my close personal friends. They have nevertheless continued to support
my pursuit and take pride in my endeavors.

And to my Jennifer:\\
Without an iota of doubt, my professional accomplishments would not
have been possible without the love and support that you have devoted to me. You
have kept me company during late night experiments. You have consoled me during
times of struggle and sadness. You have cheered my successes and announced them
atop mountains. You are my rock and my cushion. And in my seven-year pursuit of
knowledge of the unknown, I have come to only one surety - that I love you.

To all of you again - thank you.
