Carlo Yuvienco was born in New York, New York on March 22\textsuperscript{nd},
1983 to Dr. Francisco P. Yuvienco and Elizabeth T. Yuvienco. His academic and
professional pursuits would reside in New York until the time of this work,
starting with his secondary education at Stuyvesant High School. This was
followed by an undergraduate education in chemical engineering at the Cooper
Union for the Advancement of Science and Art, culminating in a Bachelor of
Engineering (granted in 2005). Carlo then was employed at Pall Corporation (East
Hills, NY) as a research scientist, working on the development of
leukocyte-reduction filtration media. After two years of industry experience,
Carlo pursued a Master of Science in biomedical engineering at the Polytechnic
Institute of New York University (granted in 2010), immediately preceding the
pursuit of his doctorate in biomedical engineering under the advisement of Prof.
Jin Kim Montclare, Ph.D. at the now New York University - Polytechnic School of
Engineering, in the Department of Chemical and Biomolecular Engineering. From
2008 to 2014, Carlo worked on several projects in the field of protein
engineering under the guidance of Prof. Montclare, having conducted experiments
in various labs within New York University, the Navy Research Laboratory, the
Wright-Patterson Air Force Base Materials and Manufacturing Directorate, and the
City University of New York. During the course of his doctoral research, he and
his research projects have been supported by the National Science Foundation
(GK-12 Program, DGE-0741714; NYU MRSEC Center, DMR-0820341; I-Corps Program,
IIP-1332165; DMR-1205384), the Air Force Office of Scientific Research
(FA-9550-07-1-0060 and FA-9550-08-1-0266), and the Army Research Office
(W911NP-10-1-0228).
